Random number generation and applications on GPU’s in R?

### 2021-10-04 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
no big changes,just to save
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@2888 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\end{leftbar}
<<echo=FALSE, results="hide", message=FALSE>>=
library("gpuR")
library("gpuRandom")
setContext(   grep('gpu', listContexts()$device_type) [1]    )
setwd("/home/ruoyong/paper1_2021_5")
@

@@

create streams on cpu
<<createStreams, size="tiny">>=
library("gpuRandom")
myStreamsCpu <- createStreamsCpu(n=4, seed = 12345)
myStreamsCpu
@

@@

check reproducibility
<<simStuff, eval=TRUE,tidy=TRUE>>=
as.vector(gpuRandom::runif(n=4, streams=myStreamsGpu1, Nglobal=c(1,nrow(myStreamsGpu1)), type = "double"))
as.vector(gpuRandom::runif(n=10, streams=myStreamsGpu2, Nglobal=c(1,nrow(myStreamsGpu1)), type = "double"))[-(1:6)]
@

>>>>

\end{leftbar}
<<echo=FALSE, results="hide", message=FALSE>>=
library("gpuR")
library("gpuRandom")
setContext(   grep('gpu', listContexts()$device_type) [1]    )
#setwd("/home/ruoyong/paper1_2021_5")
@

@@

create streams on cpu
<<createStreams, size="tiny">>=
myStreamsCpu <- createStreamsCpu(n=4, seed = 12345)
t(myStreamsCpu)
@

@@

check reproducibility
<<simStuff2, eval=TRUE,tidy=TRUE>>=
as.vector(gpuRandom::runif(n=4, streams=myStreamsGpu1, Nglobal=c(1,nrow(myStreamsGpu1)), type = "double"))
as.vector(gpuRandom::runif(n=10, streams=myStreamsGpu2, Nglobal=c(1,nrow(myStreamsGpu1)), type = "double"))[-(1:6)]
@
